---
title: "Grouped Tabsets Example"
format: html
editor: source
---

```{r}
#| include: false
reticulate::use_virtualenv(here::here("env"))
```

## Code

````md
:::{.panel-tabset group="language"}

## R

```{{r}}
data("mtcars")
mtcars$fuel_efficiency <- ifelse(mtcars$mpg > 20, "Efficient", "Not Efficient")

plot(
  mtcars$wt, mtcars$mpg,
  main = "MPG vs. Weight",
  xlab = "Weight (1000 lbs)", ylab = "MPG",
  col = ifelse(mtcars$fuel_efficiency == "Efficient", "green", "red"), pch = 19
)

legend("topright", legend = c("Efficient", "Not Efficient"), col = c("green", "red"), pch = 19)
```

## Python

```{{python}}
import pandas as pd
from plotnine import ggplot, aes, geom_point, theme_minimal

mtcars = pd.read_csv("https://raw.githubusercontent.com/mwaskom/seaborn-data/master/mpg.csv").dropna()
mtcars['fuel_efficiency'] = ['Efficient' if mpg > 20 else 'Not Efficient' for mpg in mtcars['mpg']]

plot = (
    ggplot(mtcars, aes(x='weight', y='mpg', color='fuel_efficiency')) +
    geom_point(size=3) +
    theme_minimal()
    )

plot.show()
```
:::
````

Here is the first tab:

:::{.panel-tabset group="language"}

## R

```{r}
library(ggplot2)
data("mtcars")
mtcars$fuel_efficiency <- ifelse(mtcars$mpg > 20, "Efficient", "Not Efficient")

mtcars |>
  ggplot(aes(x = wt, y = mpg, color = fuel_efficiency)) +
  geom_point(size = 3) +
  theme_minimal()
```

## Python

```{python}
import pandas as pd
from plotnine import ggplot, aes, geom_point, theme_minimal

mtcars = pd.read_csv("https://raw.githubusercontent.com/mwaskom/seaborn-data/master/mpg.csv").dropna()
mtcars['fuel_efficiency'] = ['Efficient' if mpg > 20 else 'Not Efficient' for mpg in mtcars['mpg']]

plot = (
    ggplot(mtcars, aes(x='weight', y='mpg', color='fuel_efficiency')) +
    geom_point(size=3) +
    theme_minimal()
    )

plot.show()
```

:::

Here is the second tabset:

:::{.panel-tabset group="language"}

## R

```{r}
library(gt)
towny <- gt::towny

towny_mini <- towny[order(-towny$density_2021), c("name", "website", "density_2021", "land_area_km2", "latitude", "longitude")]
towny_mini <- head(towny_mini, 10)

gt(towny)
```

## Python

```{python}
from great_tables import GT, html
from great_tables.data import towny

towny_mini = (
    towny[["name", "website", "density_2021", "land_area_km2", "latitude", "longitude"]]
    .sort_values("density_2021", ascending=False)
    .head(10)
)

(
    GT(towny_mini)
)
```
:::